---
title: "Football Players Classification Project"
author: "Mateusz Majak"
date: "5 09 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup, include=FALSE}
library(dplyr)
library(readr)
library(ggplot2)
library(tidyverse)
library(caret)
library(class)
library(tibble)
library(purrr)
library(corrplot)
library(DescTools)
library(olsrr)
library(nnet)
library(lmtest)
library(mice)
library(VIM)
library(verification)
library(janitor)
library(nnet)
library(stringr)
library(AER)
source("functions/F_accuracy_multinom.R")
library(MLmetrics)
library(kernlab)
library(verification)

players_full <- read.csv("players_20.csv",na.strings=c("","NA"))
```


#Football Players Classification

##About dataset
I decided to analyse the football players statistics scraped from 
https://sofifa.com/ and published on https://www.kaggle.com/ platform.

Sofifa publish data from FIFA game and updating it several times a year.
I chose the most fresh statistics from FIFA 20, so the whole data was as clean as
earlier updates.

Let's look on the data:
```{r}
glimpse(players_full)
```

Data contain 18278 players with 104 attributes. Some of them are IDs, urls and
names, but most are numeric values (0-100 or 1-5) describing specific skills.

##EDA and data manipulation
For classification, some of attributes will not be useful in the analysis. I
create players dataset with only useful variables.
There is also a challenge - I have to choose player position dependent variable
from 3 possible columns: team_position, player_positions, nation_position.
Not every player plays in nation cups, so I will choose between team_position
and player_positions.

```{r}
players <- 
  players_full %>% 
  dplyr::select(c(7:8,15,16,18:20,24:25,32:78))

glimpse(players)
```

56 columns left after deleting columns not good for being predictors.

Now let's compare player_positions and team_position
```{r}
ggplot(data = players) + geom_bar(mapping = aes(x = team_position))
ggplot(data = players) + geom_bar(mapping = aes(x = player_positions))
```
Team_position looks much cleaner, there are much less levels. Unofortunately the
2 largest levels are SUB and RES, which are not positions on the field. They are
refer to player status in the team (SUB is substitute and RES is injured or something
similar). Deleting such huge part of players doesn't make sense.

Player_positions has many levels, because it stores every player's position instead
of only the current. Some of levels may be contain same positions, but in different
order. I will sort them in asceding order.

```{r}
z = players$player_positions
players$player_positions <- 
  unname(sapply(z, function(z) {
    paste(sort(trimws(strsplit(z[1], ',')[[1]])), collapse=',')} ))

sort(table(players$player_positions))

```

There are many levels, but there are only field positions, so choose is as my
dependent variable.
To make it more simple and easier to look at results, I will group players into 4
main positions: Attacker, Midfielder, Defender and Goalkeeper.

```{r, include=FALSE}
players[which(
  players$player_positions=="ST"|
    players$player_positions=="LW"|
    players$player_positions=="RW"|
    players$player_positions=="CF"|
    players$player_positions=="RM,ST"|
    players$player_positions=="LW,RW"|
    players$player_positions=="LM,ST"|
    players$player_positions=="CAM,ST"|
    players$player_positions=="LM,RM,ST"|
    players$player_positions=="LW,ST"|
    players$player_positions=="RW,ST"|
    players$player_positions=="LW,RW,ST"|
    players$player_positions=="CF,ST"|
    players$player_positions=="CAM,CF"|
    players$player_positions=="LM,LW,ST"|
    players$player_positions=="CAM,LM,ST"|
    players$player_positions=="RM,RW,ST"|
    players$player_positions=="CAM,CF,ST"|
    players$player_positions=="CAM,RM,ST"|
    players$player_positions=="CAM,LW,ST"|
    players$player_positions=="CAM,CM,ST"|
    players$player_positions=="CF,RW,ST"|
    players$player_positions=="CM,ST"|
    players$player_positions=="CF,LW,ST"|
    players$player_positions=="CF,LW,RW"|
    players$player_positions=="CF,LW"|
    players$player_positions=="CAM,RW,ST"|
    players$player_positions=="CAM,CF,CM"|
    players$player_positions=="CAM,CF,LW"|
    players$player_positions=="CF,LM,ST"|
    players$player_positions=="CAM,CF,RW"|
    players$player_positions=="CF,RW"|
    players$player_positions=="CF,LM,LW"|
    players$player_positions=="CF,RM,RW"|
    players$player_positions=="LM,RW,ST"|
    players$player_positions=="CF,RM,ST"|
    players$player_positions=="LW,RM,ST"|
    players$player_positions=="CF,CM,ST"|
    players$player_positions=="CM,LW,ST"|
    players$player_positions=="CF,CM,LW"|
    players$player_positions=="LW,LWB,ST"|
    players$player_positions=="CM,RW,ST"|
    players$player_positions=="CF,LWB,ST"|
    players$player_positions=="CF,LM,RW"|
    players$player_positions=="CDM,LW,ST"),
  "player_positions"]  <- "Attacker"

players[which(
  players$player_positions=="CB"|
    players$player_positions=="LB"|
    players$player_positions=="RB"|
    players$player_positions=="RWB"|
    players$player_positions=="LWB"|
    players$player_positions=="CB,RB"|
    players$player_positions=="CB,LB"|
    players$player_positions=="CB,CDM"|
    players$player_positions=="LB,RB"|
    players$player_positions=="LB,LM"|
    players$player_positions=="RB,RM"|
    players$player_positions=="LB,LWB"|
    players$player_positions=="CB,CDM,CM"|
    players$player_positions=="RB,RWB"|
    players$player_positions=="CB,LB,RB"|
    players$player_positions=="LB,LM,LWB"|
    players$player_positions=="RB,RM,RWB"|
    players$player_positions=="CB,CDM,RB"|
    players$player_positions=="CDM,RB"|
    players$player_positions=="CDM,CM,RB"|
    players$player_positions=="LB,RB,RM"|
    players$player_positions=="CB,CM"|
    players$player_positions=="CM,RB"|
    players$player_positions=="CM,LB"|
    players$player_positions=="LM,LW,RW"|
    players$player_positions=="CB,RB,RM"|
    players$player_positions=="LM,RB,RM"|
    players$player_positions=="CM,LB,LM"|
    players$player_positions=="CDM,LB"|
    players$player_positions=="LB,LM,RM"|
    players$player_positions=="CB,LB,LWB"|
    players$player_positions=="LB,LW"|
    players$player_positions=="CB,LB,LM"|
    players$player_positions=="LB,LM,LW"|
    players$player_positions=="CDM,LB,RB"|
    players$player_positions=="LB,LM,RB"|
    players$player_positions=="CB,RB,RWB"|
    players$player_positions=="CB,CDM,LB"|
    players$player_positions=="LB,RB,RWB"|
    players$player_positions=="CB,LWB"|
    players$player_positions=="CDM,CM,LB"|
    players$player_positions=="RB,RW"|
    players$player_positions=="CDM,RB,RM"|
    players$player_positions=="LM,RM,RWB"|
    players$player_positions=="CB,RWB"|
    players$player_positions=="RB,RM,RW"|
    players$player_positions=="LB,LWB,RB"|
    players$player_positions=="CDM,LB,LM"|
    players$player_positions=="RB,RM,ST"|
    players$player_positions=="LB,RM"|
    players$player_positions=="CAM,RB"|
    players$player_positions=="CM,LB,RB"|
    players$player_positions=="CB,CM,RB"|
    players$player_positions=="CAM,LB,LM"|
    players$player_positions=="CDM,RB,RWB"|
    players$player_positions=="LB,LW,RB"|
    players$player_positions=="CB,RM"|
    players$player_positions=="CB,CM,LB"|
    players$player_positions=="LB,RB,RW"|
    players$player_positions=="CM,RB,RWB"|
    players$player_positions=="CDM,LB,LWB"|
    players$player_positions=="CB,LM,LWB"|
    players$player_positions=="LWB,RB,RWB"|
    players$player_positions=="LM,RB,RWB"|
    players$player_positions=="LB,LW,LWB"|
    players$player_positions=="CM,LB,LWB"|
    players$player_positions=="CB,LWB,RWB"|
    players$player_positions=="CB,LM,RB"|
    players$player_positions=="CB,LB,RM"|
    players$player_positions=="CB,CM,RWB"|
    players$player_positions=="CAM,CB,RB"),
  "player_positions"]  <-  "Defender"

players[which(
  players$player_positions=="CM"|
    players$player_positions=="RM"|
    players$player_positions=="LM"|
    players$player_positions=="CAM"|
    players$player_positions=="CDM"|
    players$player_positions=="CDM,CM"|
    players$player_positions=="LM,RM"|
    players$player_positions=="CAM,CM"|
    players$player_positions=="CAM,CDM,CM"|
    players$player_positions=="CAM,LM,RM"|
    players$player_positions=="CAM,LM"|
    players$player_positions=="CAM,RM"|
    players$player_positions=="RM,RW"|
    players$player_positions=="CAM,CM,LM"|
    players$player_positions=="CM,RM"|
    players$player_positions=="LM,LW"|
    players$player_positions=="CM,LM"|
    players$player_positions=="CAM,CM,RM"|
    players$player_positions=="CM,LM,RM"|
    players$player_positions=="CAM,LW"|
    players$player_positions=="CAM,RW"|
    players$player_positions=="LM,RM,RW"|
    players$player_positions=="CAM,LW,RW"|
    players$player_positions=="CAM,CM,RW"|
    players$player_positions=="LM,LW,RM"|
    players$player_positions=="CM,RB,RM"|
    players$player_positions=="CDM,CM,RM"|
    players$player_positions=="CAM,CM,RM"|
    players$player_positions=="CDM,CM,LM"|
    players$player_positions=="CAM,CDM"|
    players$player_positions=="LW,RM,RW"|
    players$player_positions=="CF,LM,RM"|
    players$player_positions=="CAM,CM,LW"|
    players$player_positions=="CAM,RM,RW"|
    players$player_positions=="CM,RW"|
    players$player_positions=="RM,RWB"|
    players$player_positions=="LM,LWB"|
    players$player_positions=="CM,LW,RW"|
    players$player_positions=="CM,LW"|
    players$player_positions=="CAM,LM,LW"|
    players$player_positions=="CAM,CF,RM"|
    players$player_positions=="CAM,CF,LM"|
    players$player_positions=="CF,RM"|
    players$player_positions=="CF,LM"|
    players$player_positions=="LW,RM"|
    players$player_positions=="LM,RW"|
    players$player_positions=="LM,LWB,RM"|
    players$player_positions=="CM,RWB"|
    players$player_positions=="CM,LM,LW"|
    players$player_positions=="LWB,RWB"|
    players$player_positions=="CM,RM,RW"|
    players$player_positions=="CM,LM,ST"|
    players$player_positions=="RM,RWB,ST"|
    players$player_positions=="RM,RW,RWB"|
    players$player_positions=="CM,LWB"|
    players$player_positions=="CF,CM,RM"|
    players$player_positions=="CF,CM"|
    players$player_positions=="CDM,LM"|
    players$player_positions=="CAM,LM,RW"|
    players$player_positions=="LW,LWB"|
    players$player_positions=="LM,RWB"|
    players$player_positions=="LM,LW,LWB"|
    players$player_positions=="CM,RM,ST"|
    players$player_positions=="CM,RM,RWB"|
    players$player_positions=="CM,LM,RW"|
    players$player_positions=="CM,LM,LWB"|
    players$player_positions=="CDM,RWB"|
    players$player_positions=="CDM,RM"|
    players$player_positions=="CAM,RM,RWB"|
    players$player_positions=="LM,LWB,RWB"|
    players$player_positions=="CDM,LM,RM"|
    players$player_positions=="CDM,CM,RWB"|
    players$player_positions=="CDM,CM,LW"|
    players$player_positions=="CAM,LW,RM"|
    players$player_positions=="CAM,LM,LWB"|
    players$player_positions=="CAM,CDM,RM"|
    players$player_positions=="CAM,CDM,LM"|
    players$player_positions=="LWB,RM,RWB"|
    players$player_positions=="LWB,RM"|
    players$player_positions=="LM,RWB,ST"|
    players$player_positions=="CM,LWB,RWB"|
    players$player_positions=="CM,LW,RM"|
    players$player_positions=="CM,LW,LWB"|
    players$player_positions=="CF,CM,LM"|
    players$player_positions=="CDM,LM,LWB"|
    players$player_positions=="CDM,LM,LW"|
    players$player_positions=="CDM,CM,ST"|
    players$player_positions=="CDM,CM,RW"|
    players$player_positions=="CDM,CM,LWB"|
    players$player_positions=="CDM,CF,CM"),
  "player_positions"]  <- "Midfielder"

players[which(
  players$player_positions=="GK"),
  "player_positions"]  <- "Goalkeeper"

players[which(
  players$player_positions!="Goalkeeper" &
    players$player_positions!="Midfielder" &
    players$player_positions!="Defender" &
    players$player_positions!="Attacker"),
  "player_positions"]  <- "Others"

```
```{r}
sort(table(players$player_positions))
```
Now we have only 69 player in Others category, which was too many different positions
to group it using such division.

I delete Others, because there is no such position on the field and it will not be
helpful in the analysis.

```{r}
players <- players[-which(players$player_positions=="Others"),]
```

I delete gk_kicking, gk_positioning, gk_diving, gk_handling,  gk_reflexes and
gk_speed because they are already represented by other columns:
goalkeeping_kicking, goalkeeping_positioning, goalkeeping_reflexes,
goalkeeping_diving, goalkeeping_handling and movement_acceleration /
movement_sprint_speed. Player_tags and player_traits are also unique values for some players -
other players do not have tags and traits - that's why I will also delete them
I delete team_position also, because it does not provide any additional
information about position.

```{r}
players <- 
  players %>% 
  dplyr::select(-c("team_position","gk_kicking","gk_positioning","gk_diving",
                   "gk_handling","gk_reflexes","gk_speed","player_tags",
                   "player_traits"))
```

Now let's look on the missing values:
```{r}
players %>% 
  md.pattern(rotate.names = TRUE)
```
There are 2036 rows with missing values in 6 columns: pace, shooting,
passing, dribbling, defending and physic. It's more than 10% of observations 
so i will omit them in the future analysis. Additionally, this values are already
represented by other variables.
```{r}
players <- 
  players %>% 
  dplyr::select(-c("pace","shooting","passing","dribbling","defending",
                   "physic"))

summary(players)
```

Most of the numerical variables are integers in 0-100 range. I will convert 
skill_moves and weak_foot from 1-5 to 0-100 range and also height_cm and 
weight_kg to 0-100 range to normalize them. It can be helpful in the future 
analysis.

```{r}
players$weak_foot   <- players$weak_foot*100/5
players$skill_moves <- players$skill_moves*100/5
players$height_cm   <- players$height_cm/(max(players$height_cm))*100
players$weight_kg   <- players$weight_kg/(max(players$weight_kg))*100

glimpse(players)
```

There are 3 character variables in the dataset: dependent variable 
player_positions, preferred_foot and work_rate. I convert them into factors and
create list of factor and numerical predictors.

```{r}
players$player_positions <- as.factor(players$player_positions)
players$preferred_foot   <- as.factor(players$preferred_foot)
players$work_rate        <- as.factor(players$work_rate)

players_numeric_vars <- 
  sapply(players, is.numeric) %>% 
  which() %>% 
  names()

players_factor_vars <- 
  sapply(players, is.factor) %>% 
  which() %>% 
  names()
```

##Data division

Now it's time to divide data into training and test set
```{r}
set.seed(987654321)

players_which_train <- createDataPartition(players$player_positions,
                                           p = 0.7, 
                                           list = FALSE) 

players_train <- players[players_which_train,]
players_test <- players[-players_which_train,]

```

The distribution of the target variable in both samples are very similar:
```{r}
players_train$player_positions %>% 
  table() %>%
  prop.table()

players_test$player_positions %>% 
  table() %>%
  prop.table()
```
Now let's look on the correlations between variables:
``` {r}
players_correlations <- 
  cor(players_train[,players_numeric_vars],
      use = "pairwise.complete.obs")

corrplot(players_correlations, 
         method = "color",tl.cex = 0.5)
```
Goalkeeping and defending variables are very highly correlated to each other.
In general, goalkeeping skills seems to be negatively correlated with most of other
attributes, so we can expect that predicting goalkeepers will be very accurate in
every model.

I save the most highly correlated variables as candidates to be excluded from 
the analysis. They can give very little information about position and increase
time consumption of computing models.
```{r}
correlated_variables_90 <- findCorrelation(players_correlations,
                cutoff = 0.90,
                names = TRUE)

correlated_variables_80 <- findCorrelation(players_correlations,
                cutoff = 0.80,
                names = TRUE)
```

Before we start modelling, let's look on the factor variables:
```{r}
ggplot(players, aes(x = preferred_foot)) + geom_bar()
ggplot(players, aes(x = work_rate)) + geom_bar()
```
We can see that there are much more players with the right foot preferred.
Only `r sum(players$preferred_foot == "Left")/sum(players$preferred_foot == "Right")*100`
of players prefer their left foot.

Work rate is rate of working in attack and defense. For example, High/Low means that
player works hard in attack and does not work hard in the defense, but it is more
mental that the real position on the field, so there are defenders with Low/Low etc.

We can see, that most of the players have Medium/Medium work rate. Other groups are
smaller, but only Low/Low seems to be really small and may not provide efficient
value to model. However, we can not add this group to another, so I will keep it.

##Data modelling
Now we are ready to try to run some models and predict players position on the field.

###Logit model

I run multinomial logit model without variables with correlation higher than 0.8
and without preferred_foot variable.
```{r}
players_mlogit1a <- multinom(player_positions ~ .,
                    data = players_train %>% 
                      dplyr::select(-c(all_of(correlated_variables_80),"preferred_foot")))

players_mlogit1a_fitted <- predict(players_mlogit1a) 

table(players_mlogit1a_fitted,
      players_train$player_positions)
```
Now I run multinomial logit model without variables with correlation higher than 0.9
and without preferred_foot variable.
```{r}
players_mlogit1b <- multinom(player_positions ~ .,
                    data = players_train %>% 
                      dplyr::select(-c(all_of(correlated_variables_90),"preferred_foot")))

players_mlogit1b_fitted <- predict(players_mlogit1b) 

table(players_mlogit1b_fitted,
      players_train$player_positions)
```

And now I run multinomial logit model with every variable.
```{r}
players_mlogit2 <- multinom(player_positions ~ .,
                    data = players_train)

players_mlogit2_fitted <- predict(players_mlogit2) 

table(players_mlogit2_fitted,
      players_train$player_positions)
```

Likelihood ratio test:
```{r}
lrtest(players_mlogit1a)[5]
lrtest(players_mlogit1b)[5]
lrtest(players_mlogit2)[5]

```
The null hypothesis can be rejected on the 0.001 level in all models.

Now I am comparing real and predicted values:

```{r}
accuracy_multinom(predicted = players_mlogit1a_fitted, 
                  real = players_train$player_positions)

accuracy_multinom(predicted = players_mlogit1b_fitted, 
                  real = players_train$player_positions)

accuracy_multinom(predicted = players_mlogit2_fitted, 
                  real = players_train$player_positions)
```
Multinomial logit model without variables with correlation higher than 0.9
and without preferred_foot variable has the highest accuracy - 87.72356.
Accuracy is pretty high, but can it be higher? Let's find out.

###KNN model

I will start from the defining the training controls - it will be no 
cross validation and 10-fold cross validation control. I will compare the models
with and without cross validation.

```{r}
control_nocv <- trainControl(method = "none")

control_cv10 <- trainControl(method = "cv",
                          number = 10,
                          classProbs = TRUE)
```

Now I compute 4 models - two without cross validation and two with cross 
validation (full data and data with highly correlated variables and 
preferred_foot variable excluded).

I try many k values to obtain possibly highest accuracy and scale all variables 
to range [0, 1].
```{r}
set.seed(987654321)

test_k <- data.frame(k = seq(1, 99, 4))

players_train_knn1a <- 
  train(player_positions ~ .,
        data = players_train %>% 
          dplyr::select(-c(all_of(correlated_variables_90),"preferred_foot")),
        method = "knn",
        trControl = control_nocv,
        tuneGrid = test_k,
        preProcess = c("range"))

players_train_knn1b <- 
  train(player_positions ~ .,
        data = players_train,
        method = "knn",
        trControl = control_nocv,
        tuneGrid = test_k,
        preProcess = c("range"))

players_train_knn2a <- 
  train(player_positions ~ .,
        data = players_train %>% 
          dplyr::select(-c(all_of(correlated_variables_90),"preferred_foot")),
        method = "knn",
        trControl = control_cv10,
        tuneGrid = test_k,
        preProcess = c("range"))

players_train_knn2b <- 
  train(player_positions ~ .,
        data = players_train,
        method = "knn",
        trControl = control_cv10,
        tuneGrid = test_k,
        preProcess = c("range"))

par(mfrow=c(2,2))
plot(players_train_knn1a)
plot(players_train_knn1b)
plot(players_train_knn2a)
plot(players_train_knn2b)
```

And let's look on the accuracy of each model:
```{r}
players_test_forecasts <- 
  data.frame(players_train_knn1a = predict(players_train_knn1a,
                                         players_test),
             players_train_knn1b = predict(players_train_knn1b,
                                        players_test),
             players_train_knn2a = predict(players_train_knn2a,
                                          players_test),
             players_train_knn2b = predict(players_train_knn2b,
                                                 players_test))

sapply(players_test_forecasts,
       function(x) accuracy_multinom(predicted = x,
                                        real = players_test$player_positions))
```


###SVM model

Training controls are already defined. I would like to try many parameters 
values to find the best one so I create grids of parameters for polynomial and 
radial basis kernel:
```{r}
svm_parametersPoly <- expand.grid(C = c(0.001, 0.01, 0.05, 0.1, 0.5, 1),
                                  degree = 2:5, 
                                  scale = 1)

parametersC_sigma <- 
  expand.grid(C = c(0.01, 0.05, 0.1, 0.5, 1, 5, 10, 25, 50, 100),
              sigma = c(0.05, 0.1, 0.2, 0.5, 1, 10, 100, 1000))
```

```{r}
set.seed(987654321)

data1.svm_poly <- train(group ~ X1 + X2, 
                        data = data1_train, 
                        method = "svmPoly",
                        tuneGrid = svm_parametersPoly,
                        trControl = ctrl_cv5x3)

data1.svm_poly

plot(data1.svm_poly$finalModel)

data1_test$fore_svm_poly <- predict(data1.svm_poly, 
                                    newdata = data1_test)

confusionMatrix(data1_test$fore_svm_poly,
                data1_test$group,
                positive = "1")

data1.svm_Radial1 <- train(group ~ X1 + X2,
                           data = data1_train, 
                           method = "svmRadial",
                           tuneGrid = parametersC_sigma,
                           trControl = ctrl_cv5x3)

data1.svm_Radial1

data1.svm_Radial1$finalModel

plot(data1.svm_Radial1$finalModel)

data1_test$fore_svm_Radial1 <- predict(data1.svm_Radial1, 
                                       newdata = data1_test)

confusionMatrix(data1_test$fore_svm_Radial1,
                data1_test$group,
                positive = "1")

```










```{r, echo=FALSE}
plot(pressure)
```

