---
title: "Coffee Cupper Points Prediction"
author: "Mateusz Majak"
date: "14.09.2020"
output: 
  html_document:
    number_sections: true
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(readr)
library(ggplot2)
library(caret)
library(class)
library(tibble)
library(purrr)
library(corrplot)
library(DescTools)
library(olsrr)
library(mice)
library(VIM)
library(verification)
library(janitor)
library(nnet)
source("functions/F_regression_metrics.r")
setwd("C:/Users/mateu/Documents/GIT/ProjectsML1")

coffee_full <- read.csv("arabica_data_cleaned.csv",na.strings=c("","NA"))
```

# About dataset

I decided to analyse the arabica coffees statistics scraped from 
the Coffee Quality Institute dataset and published by James LeDoux on https://github.com/jldbc/coffee-quality-database.

Coffee Quality Institute runs a Q Program, which identifies quality coffees across
the World. One of the target of program is possibility of comparising coffees from
other continents.

Let's look on the data:
```{r}
glimpse(coffee_full)
```
Data contain 1311 coffees with 44 attributes. Some of them are IDs, names, and
small regions (unique almost), but most are numeric and categorical variables 
describing specific parameters quality and parameters of production.

# EDA and data manipulation

I create coffee dataset without clumsy data like row numbers, Lot.Number, 
unique codes and columns with the same information.
```{r}

coffee <- coffee_full
coffee[,c("X","Species","Certification.Address","Certification.Contact",
          "Lot.Number","Mill","ICO.Number","Expiration","Grading.Date",
          "Company","Farm.Name","Owner","Producer","Owner.1",
          "In.Country.Partner","Region","Altitude","Certification.Body",
          "Harvest.Year")] <- NULL
```

## Missing values

Now let's look on the missing values:
```{r fig.width=12}
colSums(is.na(coffee)) %>% 
  sort()

coffee %>% 
  md.pattern(rotate.names = TRUE)
```
There are 1 NA in Quakers column and 227 NAs in each altitude column.

Dealing with missing value in Quakers column (I replace the missing value with 
the median):
```{r}
table(coffee$Quakers, useNA = "ifany")

coffee$Quakers[is.na(coffee$Quakers)] <- median(coffee$Quakers, na.rm=TRUE)
```

Dealing with missing values in altitudes columns:
```{r message=FALSE, warning=FALSE}
ggplot(coffee,
       aes(x = altitude_low_meters)) +
  geom_histogram(fill = "blue",
                 bins = 100) +
  theme_bw()
```

There are 227 out of 1311 rows with NA altitudes.There are also 4 clear outliers 
- let's see them:
```{r}
which(coffee$altitude_low_meters>=11000)
which(coffee$altitude_high_meters>=11000)
which(coffee$altitude_mean_meters>=11000)
```
They are the same rows.

I assign outliers to the altitude_outliers vector:
```{r}
altitude_outliers <- which(coffee$altitude_low_meters>=11000)

coffee[altitude_outliers,]
```

Interesting information - Geisha coffee is one of the best and most expensive 
coffee in the world. It is grown at high mountains. There is a farm Café Takesi 
in Bolivia, that claims to be the world’s highest coffee farm, at an elevation 
of 1,900 to 2,500 meters above sea level.

For us, it means that we should probably treat each value above 2500m as an outlier.
There are values very close to 2500m, so I will cut every value above 2650m.
```{r}
altitude_outliers <- which(coffee$altitude_low_meters>=2650)
altitude_outliers <- which(coffee$altitude_high_meters>=2650)
altitude_outliers <- which(coffee$altitude_mean_meters>=2650)

coffee[altitude_outliers,]
```

The rest of the data containing altitude outliers looks reliably. Thus, I will 
group outliers together with NAs - there is no possibility of coffee growing at 
such high altitudes.
```{r}
coffee[altitude_outliers,"altitude_low_meters"]  <- NA
coffee[altitude_outliers,"altitude_high_meters"] <- NA
coffee[altitude_outliers,"altitude_mean_meters"] <- NA
```

Now I try to deal with NAs using multiple methods replace missings for 
altitudes with sample average:
```{R}
coffee <- coffee %>% 
  mutate(altitude_low_meters.impute_mean = ifelse(is.na(altitude_low_meters), 
                                                  mean(altitude_low_meters, 
                                                       na.rm = TRUE),
                                                  altitude_low_meters),
         altitude_high_meters.impute_mean = ifelse(is.na(altitude_high_meters), 
                                                  mean(altitude_high_meters,
                                                       na.rm = TRUE),
                                                  altitude_high_meters),
         altitude_mean_meters.impute_mean = ifelse(is.na(altitude_mean_meters), 
                                                   mean(altitude_mean_meters,
                                                        na.rm = TRUE),
                                                   altitude_mean_meters)
         )


coffee <- coffee %>% 
  mutate(altitude_low_meters.impute_median = ifelse(is.na(altitude_low_meters), 
                                                  median(altitude_low_meters,
                                                         na.rm = TRUE),
                                                  altitude_low_meters),
         altitude_high_meters.impute_median = ifelse(is.na(altitude_high_meters), 
                                                     median(altitude_high_meters,
                                                            na.rm = TRUE),
                                                     altitude_high_meters),
         altitude_mean_meters.impute_median = ifelse(is.na(altitude_mean_meters),
                                                     median(altitude_mean_meters,
                                                            na.rm = TRUE),
                                                     altitude_mean_meters)
  )

coffee <- coffee %>% 
  group_by(Country.of.Origin) %>%
  mutate(altitude_low_meters.impute.Gmean = ifelse(is.na(altitude_low_meters),
                                                   mean(altitude_low_meters,
                                                        na.rm = TRUE),
                                                   altitude_low_meters),
         altitude_low_meters.impute.Gmed = ifelse(is.na(altitude_low_meters),
                                                  median(altitude_low_meters,
                                                         na.rm = TRUE),
                                                  altitude_low_meters),
         altitude_high_meters.impute.Gmean = ifelse(is.na(altitude_high_meters),
                                                    median(altitude_high_meters,
                                                           na.rm = TRUE),
                                                    altitude_high_meters),
         altitude_high_meters.impute.Gmed = ifelse(is.na(altitude_high_meters), 
                                                   mean(altitude_high_meters,
                                                        na.rm = TRUE),
                                                   altitude_high_meters),
         altitude_mean_meters.impute.Gmean = ifelse(is.na(altitude_mean_meters),
                                                    median(altitude_mean_meters,
                                                           na.rm = TRUE),
                                                    altitude_mean_meters),
         altitude_mean_meters.impute.Gmed = ifelse(is.na(altitude_mean_meters), 
                                                   mean(altitude_mean_meters,
                                                        na.rm = TRUE),
                                                   altitude_mean_meters)
  ) %>% ungroup()

coffee %>%
  dplyr::select(starts_with("altitude")) %>%
  summary()
```

Impute_median seems to be the closest imputations to the original dataset means 
and medians in subgroups do not give better results.Thus, since now we will use altitude_high_meters.impute_median, altitude_low_meters.impute_median and altitude_mean_meters.impute_median.

```{r}
coffee$altitude_low_meters.impute.Gmean   <- NULL
coffee$altitude_mean_meters.impute.Gmean  <- NULL
coffee$altitude_high_meters.impute.Gmean  <- NULL
coffee$altitude_low_meters.impute.Gmed    <- NULL
coffee$altitude_high_meters.impute.Gmed   <- NULL
coffee$altitude_mean_meters.impute.Gmed   <- NULL
```

NAs in Factor columns:
```{r}
colSums(is.na(coffee)) %>% 
  sort()
```
## Data transformation

Let's look on the Country.of.Origin:
```{r}
table(coffee$Country.of.Origin)
```
There is one coffee without name of the Country of origin. I use mode to input 
the name:
```{r}
coffee <- coffee %>% 
  dplyr::mutate(Country.of.Origin.impute.Gmode = if_else(is.na(Country.of.Origin),
                                        Mode(Country.of.Origin, na.rm = TRUE),
                                        Country.of.Origin))
```
Colombia assigned to NA. Only one observation was changed, so the distribution of Country.of.Origin.impute.Gmode is very close to the the distribution of 
Country.of.Origin. Thus, I will use Country.of.Origin.impute.Gmode in the 
future analysis.

Maybe the region will be more helpful that country, so I create Region column:
```{r}
table(coffee$Country.of.Origin.impute.Gmode)
coffee[,"Region"] <- NA
coffee$Region <- as.character(coffee$Region)

coffee$Country.of.Origin.impute.Gmode <- 
  as.character(coffee$Country.of.Origin.impute.Gmode)
#East Africa group
coffee[which(coffee$Country.of.Origin.impute.Gmode=="Zambia"|
               coffee$Country.of.Origin.impute.Gmode=="Uganda"|
               coffee$Country.of.Origin.impute.Gmode=="Burundi"|
               coffee$Country.of.Origin.impute.Gmode=="Rwanda"|
               coffee$Country.of.Origin.impute.Gmode=="Malawi"|
               coffee$Country.of.Origin.impute.Gmode=="Papua New Guinea"|
               coffee$Country.of.Origin.impute.Gmode=="Mauritius"|
               coffee$Country.of.Origin.impute.Gmode=="Ethiopia"|
               coffee$Country.of.Origin.impute.Gmode=="Kenya"
             ),
       "Region"] <- "East Africa"

#West Africa
coffee[which(coffee$Country.of.Origin.impute.Gmode=="Tanzania, United Republic Of"|
               coffee$Country.of.Origin.impute.Gmode=="Cote d?Ivoire"
             ),
       "Region"] <- "West Africa"

#Asia and Oceania
coffee[which(coffee$Country.of.Origin.impute.Gmode=="Japan"|
               coffee$Country.of.Origin.impute.Gmode=="Thailand"|
               coffee$Country.of.Origin.impute.Gmode=="Vietnam"|
               coffee$Country.of.Origin.impute.Gmode=="Myanmar"|
               coffee$Country.of.Origin.impute.Gmode=="Philippines"|
               coffee$Country.of.Origin.impute.Gmode=="Laos"|
               coffee$Country.of.Origin.impute.Gmode=="China"|
               coffee$Country.of.Origin.impute.Gmode=="India"|
               coffee$Country.of.Origin.impute.Gmode=="Taiwan"|
               coffee$Country.of.Origin.impute.Gmode=="Indonesia"|
               coffee$Country.of.Origin.impute.Gmode=="Papua New Guinea"),
       "Region"] <- "Asia and Oceania"

#Central America
coffee[which(coffee$Country.of.Origin.impute.Gmode=="Costa Rica"|
               coffee$Country.of.Origin.impute.Gmode=="Guatemala"|
               coffee$Country.of.Origin.impute.Gmode=="Haiti"|
               coffee$Country.of.Origin.impute.Gmode=="Honduras"|
               coffee$Country.of.Origin.impute.Gmode=="Nicaragua"|
               coffee$Country.of.Origin.impute.Gmode=="El Salvador"|
               coffee$Country.of.Origin.impute.Gmode=="Panama"
             ),
       "Region"] <- "Central America"

#South America
coffee[which(coffee$Country.of.Origin.impute.Gmode=="Peru"|
               coffee$Country.of.Origin.impute.Gmode=="Ecuador"|
               coffee$Country.of.Origin.impute.Gmode=="Brazil"|
               coffee$Country.of.Origin.impute.Gmode=="Colombia"
             ),
       "Region"] <- "South America"
#North America
coffee[which(coffee$Country.of.Origin.impute.Gmode=="Mexico"|
               coffee$Country.of.Origin.impute.Gmode=="United States"|
               coffee$Country.of.Origin.impute.Gmode=="United States (Hawaii)"|
               coffee$Country.of.Origin.impute.Gmode=="United States (Puerto Rico)"
             ),
       "Region"] <- "North America"

coffee$Region <- as.factor(coffee$Region)

coffee$Country.of.Origin.impute.Gmode <- 
  as.factor(coffee$Country.of.Origin.impute.Gmode)
```

Now let's look on the Bag.Weight factor:
```{r}
table(coffee$Bag.Weight)
coffee$Bag.Weight <- as.character(coffee$Bag.Weight)
```

There are two types of measurement - we should convert lbs to the kg.
```{r}
coffee[which(coffee$Bag.Weight=="1 lbs"),"Bag.Weight"]    <- "<=1"
coffee[which(coffee$Bag.Weight=="100 lbs"),"Bag.Weight"]  <- "45"
coffee[which(coffee$Bag.Weight=="130 lbs"),"Bag.Weight"]  <- "58.5"
coffee[which(coffee$Bag.Weight=="132 lbs"),"Bag.Weight"]  <- "59.4"
coffee[which(coffee$Bag.Weight=="150 lbs"),"Bag.Weight"]  <- "67.5"
coffee[which(coffee$Bag.Weight=="2 lbs"),"Bag.Weight"]    <- "<=1"
coffee[which(coffee$Bag.Weight=="55 lbs"),"Bag.Weight"]   <- "24.75"
coffee[which(coffee$Bag.Weight=="80 lbs"),"Bag.Weight"]   <- "36"
coffee[which(coffee$Bag.Weight=="0 kg"),"Bag.Weight"]     <- "<=1"
coffee[which(coffee$Bag.Weight=="0 lbs"),"Bag.Weight"]    <- "<=1"
coffee[which(coffee$Bag.Weight=="1"),"Bag.Weight"]        <- "<=1"
coffee[which(coffee$Bag.Weight=="1 kg"),"Bag.Weight"]     <- "<=1"
coffee[which(coffee$Bag.Weight=="1 kg,lbs"),"Bag.Weight"] <- "<=1"
coffee[which(coffee$Bag.Weight=="10 kg"),"Bag.Weight"]    <- "(1;10>"
coffee[which(coffee$Bag.Weight=="2"),"Bag.Weight"]        <- "(1;10>"
coffee[which(coffee$Bag.Weight=="2 kg"),"Bag.Weight"]     <- "(1;10>"
coffee[which(coffee$Bag.Weight=="2 kg,lbs"),"Bag.Weight"] <- "(1;10>"
coffee[which(coffee$Bag.Weight=="3 kg"),"Bag.Weight"]     <- "(1;10>"
coffee[which(coffee$Bag.Weight=="3 lbs"),"Bag.Weight"]    <- "(1;10>"
coffee[which(coffee$Bag.Weight=="4 lbs"),"Bag.Weight"]    <- "(1;10>"
coffee[which(coffee$Bag.Weight=="5 lbs"),"Bag.Weight"]    <- "(1;10>"
coffee[which(coffee$Bag.Weight=="4 kg"),"Bag.Weight"]     <- "(1;10>"
coffee[which(coffee$Bag.Weight=="5 kg"),"Bag.Weight"]     <- "(1;10>"
coffee[which(coffee$Bag.Weight=="6 kg"),"Bag.Weight"]     <- "(1;10>"
coffee[which(coffee$Bag.Weight=="6"),"Bag.Weight"]        <- "(1;10>"
coffee[which(coffee$Bag.Weight=="8 kg"),"Bag.Weight"]     <- "(1;10>"

coffee[which(coffee$Bag.Weight=="100 lbs"),"Bag.Weight"]  <- "(10;60>"
coffee[which(coffee$Bag.Weight=="130 lbs"),"Bag.Weight"]  <- "(10;60>"
coffee[which(coffee$Bag.Weight=="132 lbs"),"Bag.Weight"]  <- "(10;60>"
coffee[which(coffee$Bag.Weight=="15 kg"),"Bag.Weight"]    <- "(10;60>"
coffee[which(coffee$Bag.Weight=="18 kg"),"Bag.Weight"]    <- "(10;60>"
coffee[which(coffee$Bag.Weight=="20 kg"),"Bag.Weight"]    <- "(10;60>"
coffee[which(coffee$Bag.Weight=="24 kg"),"Bag.Weight"]    <- "(10;60>"
coffee[which(coffee$Bag.Weight=="25 kg"),"Bag.Weight"]    <- "(10;60>"
coffee[which(coffee$Bag.Weight=="29 kg"),"Bag.Weight"]    <- "(10;60>"
coffee[which(coffee$Bag.Weight=="30 kg"),"Bag.Weight"]    <- "(10;60>"
coffee[which(coffee$Bag.Weight=="34 kg"),"Bag.Weight"]    <- "(10;60>"
coffee[which(coffee$Bag.Weight=="35 kg"),"Bag.Weight"]    <- "(10;60>"
coffee[which(coffee$Bag.Weight=="40 kg"),"Bag.Weight"]    <- "(10;60>"
coffee[which(coffee$Bag.Weight=="46 kg"),"Bag.Weight"]    <- "(10;60>"
coffee[which(coffee$Bag.Weight=="50 kg"),"Bag.Weight"]    <- "(10;60>"
coffee[which(coffee$Bag.Weight=="59 kg"),"Bag.Weight"]    <- "(10;60>"
coffee[which(coffee$Bag.Weight=="60 kg"),"Bag.Weight"]    <- "(10;60>"
coffee[which(coffee$Bag.Weight=="45"),"Bag.Weight"]       <- "(10;60>"
coffee[which(coffee$Bag.Weight=="67.5"),"Bag.Weight"]     <- "(10;60>"
coffee[which(coffee$Bag.Weight=="59.4"),"Bag.Weight"]     <- "(10;60>"
coffee[which(coffee$Bag.Weight=="58.5"),"Bag.Weight"]     <- "(10;60>"
coffee[which(coffee$Bag.Weight=="36"),"Bag.Weight"]       <- "(10;60>"
coffee[which(coffee$Bag.Weight=="59.4"),"Bag.Weight"]     <- "(10;60>"
coffee[which(coffee$Bag.Weight=="24.75"),"Bag.Weight"]    <- "(10;60>"

coffee[which(coffee$Bag.Weight=="100 kg"),"Bag.Weight"]   <- ">60"
coffee[which(coffee$Bag.Weight=="12000 kg"),"Bag.Weight"] <- ">60"
coffee[which(coffee$Bag.Weight=="1218 kg"),"Bag.Weight"]  <- ">60"
coffee[which(coffee$Bag.Weight=="13800 kg"),"Bag.Weight"] <- ">60"
coffee[which(coffee$Bag.Weight=="150 lbs"),"Bag.Weight"]  <- ">60"
coffee[which(coffee$Bag.Weight=="1500 kg"),"Bag.Weight"]  <- ">60"
coffee[which(coffee$Bag.Weight=="18000 kg"),"Bag.Weight"] <- ">60"
coffee[which(coffee$Bag.Weight=="18975 kg"),"Bag.Weight"] <- ">60"
coffee[which(coffee$Bag.Weight=="19200 kg"),"Bag.Weight"] <- ">60"
coffee[which(coffee$Bag.Weight=="350 kg"),"Bag.Weight"]   <- ">60"
coffee[which(coffee$Bag.Weight=="66 kg"),"Bag.Weight"]    <- ">60"
coffee[which(coffee$Bag.Weight=="660 kg"),"Bag.Weight"]   <- ">60"
coffee[which(coffee$Bag.Weight=="67 kg"),"Bag.Weight"]    <- ">60"
coffee[which(coffee$Bag.Weight=="69 kg"),"Bag.Weight"]    <- ">60"
coffee[which(coffee$Bag.Weight=="70 kg"),"Bag.Weight"]    <- ">60"
coffee[which(coffee$Bag.Weight=="9000 kg"),"Bag.Weight"]  <- ">60"
coffee[which(coffee$Bag.Weight=="80 kg"),"Bag.Weight"]    <- ">60"

coffee$Bag.Weight <- factor(coffee$Bag.Weight)
```

Now let's look on the Processing.Method factor:
```{r}
table(coffee$Processing.Method)
```

I group NA and Other together.
```{R}
coffee$Processing.Method <- addNA(coffee$Processing.Method)
levels(coffee$Processing.Method)
coffee[which(coffee$Processing.Method=="Other"),"Processing.Method"] <- NA
coffee$Processing.Method <- droplevels(coffee$Processing.Method)
coffee$Processing.Method <- as.character(coffee$Processing.Method)
```

Now let's deal with missing values.
```{r}
coffee <- coffee %>% 
  group_by(Region) %>%
  mutate(Processing.Method.impute.Gmode = if_else(is.na(Processing.Method),
                                                  Mode(Processing.Method, na.rm = TRUE),
                                                  Processing.Method)) %>%
  ungroup()

coffee$Processing.Method <- as.factor(coffee$Processing.Method)

coffee$Processing.Method.impute.Gmode <- 
  as.factor(coffee$Processing.Method.impute.Gmode)

coffee$Processing.Method.impute.Gmode <- 
  addNA(coffee$Processing.Method.impute.Gmode)

coffee$Processing.Method.impute.Gmode <- 
  droplevels(coffee$Processing.Method.impute.Gmode)

coffee$Processing.Method %>% 
  table() %>%
  prop.table()

coffee$Processing.Method.impute.Gmode %>%
  table() %>%
  prop.table()
```
Distributions are quite similar.

There are only NAs in Color and Variety color left.Let's look on the next 
factor - Color.
```{r}
coffee$Color <- addNA(coffee$Color)
table(coffee$Color)
```

I should group NA and None together. Blue-Green and Bluish-Green are the 
same colors, thus I group them.
```{r}
coffee[which(coffee$Color=="None"),"Color"] <- NA
coffee[which(coffee$Color=="Blue-Green"),"Color"] <- "Bluish-Green"
coffee$Color <- droplevels(coffee$Color)
table(coffee$Color)
coffee$Color <- as.character(coffee$Color)

#267 NA values
coffee <- coffee %>% 
  group_by(Region) %>%
  mutate(Color.impute.Gmode = if_else(is.na(Color),
                                      (Mode(Color, na.rm = TRUE)),
                                      Color)) %>%
  ungroup()


coffee$Color.impute.Gmode <- addNA(coffee$Color.impute.Gmode)
table(coffee$Color.impute.Gmode)

coffee$Color %>% 
  table() %>%
  prop.table()

coffee$Color.impute.Gmode %>%
  table() %>%
  prop.table()

coffee$Color.impute.Gmode <- droplevels(coffee$Color.impute.Gmode)
table(coffee$Color.impute.Gmode)
```

Now it's time to look on the last factor - Variety.
```{r}
coffee$Variety <- as.character(coffee$Variety)
```

108 Other and 201 NA - I group them.
```{r}
coffee[which(coffee$Variety=="Other"),"Variety"] <- NA
coffee$Variety <- addNA(coffee$Variety)
table(coffee$Variety)
```

Now I group small groups into bigger groups based on information from https://varieties.worldcoffeeresearch.org/.
```{r}
coffee$Variety <- as.character(coffee$Variety)

coffee[which(coffee$Variety=="Java"),"Variety"]                  <- "Ethiopian Landrace"
coffee[which(coffee$Variety=="Gesha"),"Variety"]                 <- "Ethiopian Landrace"
coffee[which(coffee$Variety=="Ethiopian Heirlooms"),"Variety"]   <- "Ethiopian Landrace"
coffee[which(coffee$Variety=="Ethiopian Yirgacheffe"),"Variety"] <- "Ethiopian Landrace"
coffee[which(coffee$Variety=="Ruiru 11"),"Variety"]              <- "Introgressed"
coffee[which(coffee$Variety=="Catimor"),"Variety"]               <- "Introgressed"
coffee[which(coffee$Variety=="Arusha"),"Variety"]                <- "Typica"
coffee[which(coffee$Variety=="Blue Mountain"),"Variety"]         <- "Typica"
coffee[which(coffee$Variety=="Mandheling"),"Variety"]            <- "Typica"
coffee[which(coffee$Variety=="Marigojipe"),"Variety"]            <- "Typica"
coffee[which(coffee$Variety=="Pache Comun"),"Variety"]           <- "Typica"
coffee[which(coffee$Variety=="Peaberry"),"Variety"]              <- "Typica"
coffee[which(coffee$Variety=="SL14"),"Variety"]                  <- "Typica"
coffee[which(coffee$Variety=="SL34"),"Variety"]                  <- "Typica"
coffee[which(coffee$Variety=="Sulawesi"),"Variety"]              <- "Typica"
coffee[which(coffee$Variety=="Catuai"),"Variety"]                <- "Bourbon-Typica cross"
coffee[which(coffee$Variety=="Mundo Novo"),"Variety"]            <- "Bourbon-Typica cross"
coffee[which(coffee$Variety=="Pacamara"),"Variety"]              <- "Bourbon-Typica cross"
coffee[which(coffee$Variety=="SL28"),"Variety"]                  <- "Bourbon-Typica cross"
coffee[which(coffee$Variety=="Sumatra"),"Variety"]               <- "Bourbon-Typica cross"
coffee[which(coffee$Variety=="Sumatra Lintong"),"Variety"]       <- "Bourbon-Typica cross"
coffee[which(coffee$Variety=="Moka Peaberry"),"Variety"]         <- "Bourbon"
coffee[which(coffee$Variety=="Pacas"),"Variety"]                 <- "Bourbon"

coffee <- coffee %>% 
  group_by(Region, Color.impute.Gmode) %>%
  mutate(Variety.impute.Gmode = if_else(is.na(Variety),
                                      Mode(Variety, na.rm = TRUE),
                                      Variety)) %>%
  ungroup()

coffee$Variety %>% 
  table() %>%
  prop.table()

coffee$Variety.impute.Gmode %>%
  table() %>%
  prop.table()

coffee$Variety <- as.factor(coffee$Variety)
coffee$Variety <- droplevels(coffee$Variety)
coffee$Variety <- addNA(coffee$Variety)
table(coffee$Variety)

coffee$Variety.impute.Gmode <- addNA(coffee$Variety.impute.Gmode)
coffee$Variety.impute.Gmode <- as.factor(coffee$Variety.impute.Gmode)
coffee$Variety.impute.Gmode <- droplevels(coffee$Variety.impute.Gmode)
table(coffee$Variety.impute.Gmode)

coffee$Variety.impute.Gmode %>% 
  table() %>%
  prop.table()

coffee$Variety <- as.character(coffee$Variety)

coffee$Variety %>%
  table() %>%
  prop.table()
  
coffee$Variety <- as.factor(coffee$Variety)
```
Distribution has changed, but Typica and Bourbon varieties are most popular  in 
the World, so it is very likely to be truth.

Now let's look for outliers considering Total.Cup.Points result.
```{r}
ggplot(coffee,
       aes(x = Total.Cup.Points)) +
  geom_histogram(fill = "blue",
                 bins = 100) +
  theme_bw()
```

There is one outlier in Total.Cup.Points:
```{r}
coffee[which(coffee$Total.Cup.Points==0),]
```

The other numeric variables are equal to 0, so I delete this observation
```{r}
coffee <- coffee[-which(coffee$Total.Cup.Points==0),]
```

I create new dataframe without variables which I will not use in the analysis. I 
also delete Total.Cup.Points, because it is the sum of Aroma, Flavor, Aftertaste, 
Acidity, Body, Balance,Uniformity, Clean.Cup, Sweetness and Cupper.Points.
```{r}
coffee_final <- coffee
coffee_final[,c("Country.of.Origin","Processing.Method","Variety",
                "altitude_low_meters","altitude_high_meters",
             "altitude_mean_meters","Color","altitude_mean_meters.impute_mean",
             "altitude_low_meters.impute_mean",
             "altitude_high_meters.impute_mean","Total.Cup.Points")] <- NULL
```

Before split the dataset, I check if there are variables with zero or near zero 
variance, because such variables may need some tranformations.
```{r}
nearZeroVar(coffee_final,
            saveMetrics = TRUE) -> coffees_nzv_stats

coffees_nzv_stats %>% 
  rownames_to_column("variable") %>% 
  arrange(-zeroVar, -nzv, -freqRatio)
```

We havee 3 problematic variables
```{r}
table(coffee_final$Quakers)
table(coffee_final$Clean.Cup)
table(coffee_final$Sweetness)
```

I will group them in two groups, because in each column there is one hugly 
dominant value.
```{r}
quakers_not_zero_train <- which(coffee_final$Quakers>0)
coffee_final$Quakers <- as.character(coffee_final$Quakers)
coffee_final[quakers_not_zero_train,"Quakers"] <- ">0"
coffee_final$Quakers <- as.factor(coffee_final$Quakers)
table(coffee_final$Quakers)

clean_cup_not_10_train <- which(coffee_final$Clean.Cup<10)
coffee_final$Clean.Cup <- as.character(coffee_final$Clean.Cup)
coffee_final[clean_cup_not_10_train,"Clean.Cup"] <- "<10"
coffee_final$Clean.Cup <- as.factor(coffee_final$Clean.Cup)
table(coffee_final$Clean.Cup)

sweetness_not_10_train <- which(coffee_final$Sweetness<10)
coffee_final$Sweetness <- as.character(coffee_final$Sweetness)
coffee_final[sweetness_not_10_train,"Sweetness"] <- "<10"
coffee_final$Sweetness <- as.factor(coffee_final$Sweetness)
table(coffee_final$Sweetness)
```

Let's check if they have still near zero variance:
```{r}
nearZeroVar(coffee_final,
            saveMetrics = TRUE) -> coffees_nzv_stats

coffees_nzv_stats %>% 
  rownames_to_column("variable") %>% 
  arrange(-zeroVar, -nzv, -freqRatio)
```
There are no near zero variance variables now.

## Data division

Now let's divide the set into learning and testing sample
```{r warning=FALSE}
set.seed(987654321)

coffees_which_train <- createDataPartition(coffee_final$Cupper.Points,
                                          p = 0.7, 
                                          list = FALSE) 
head(coffees_which_train)

coffees_train <- coffee_final[coffees_which_train,]
coffees_test <- coffee_final[-coffees_which_train,]
```

The distributions of the target variable in both samples are similar:
```{r}
summary(coffees_train$Cupper.Points)
summary(coffees_test$Cupper.Points)
```

Storing the list of names of numeric variables into a vector:
```{r}
coffees_numeric_vars <- 
  sapply(coffees_train, is.numeric) %>% 
  which() %>% 
  names()

coffees_numeric_vars
```
## Correlation

Mutually correlated variables:
```{r}
coffee_correlations <- 
  cor(coffees_train[,coffees_numeric_vars],
      use = "pairwise.complete.obs")

coffees_numeric_vars_order <- 
  coffee_correlations[,"Cupper.Points"] %>% 
  sort(decreasing = TRUE) %>%
  names()

corrplot.mixed(coffee_correlations[coffees_numeric_vars_order, 
                                   coffees_numeric_vars_order],
               upper = "circle",
               lower = "pie",
               tl.col="black",
               tl.pos = "lt",
               tl.cex = 0.6)
```

We can see very high correlation between altitude variables. Number of bags and Category.One.Defects seem to have very small correlation between them and the 
other variables - we will skip them.
```{r}
corrplot.mixed(coffee_correlations[coffees_numeric_vars_order[-12:-13], 
                                   coffees_numeric_vars_order[-12:-13]],
               upper = "circle",
               lower = "pie",
               tl.col = "black",
               tl.pos = "lt",
               tl.cex = 0.6)
```
## Variables relationships

The relation of the target variable with the most strongly correlated variables 
- Flavour:
```{r fig.width=5, fig.height=4}
ggplot(coffees_train,
       aes(x = Cupper.Points,
           y = Flavor)) +
  geom_point(col = "blue") +
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw()
```

5 coffees clearly not matching the relationship - 2 coffees with the flavour < 8, 
but Cupper.Points = 10. 3 coffees with Cupper.Points < 5.5 and Flavor > 7.5.
Maybe exclude these observations from the sample.
```{r}
coffees_outliers <- NULL
coffees_outliers_flavor <- which(coffees_train$Flavor < 8 &
                                   coffees_train$Cupper.Points == 10)
coffees_outliers_flavor <- append(coffees_outliers_flavor,
                                  which(coffees_train$Flavor > 7.5 &
                                          coffees_train$Cupper.Points < 5.5))

coffees_outliers <- append(coffees_outliers,coffees_outliers_flavor)
```

Aftertaste:
```{r fig.width=5, fig.height=4}
ggplot(coffees_train,
       aes(x = Cupper.Points,
           y = Aftertaste)) +
  geom_point(col = "blue") +
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw()
```

5 coffees clearly notmatching the relationship - they look similar to the 
previous values from Flavor.

```{r}
coffees_outliers_aftertaste <- which(coffees_train$Aftertaste >= 7.5 &
                                       coffees_train$Cupper.Points < 5.5)
coffees_outliers_aftertaste <- append(coffees_outliers_aftertaste,
                                      which(coffees_train$Aftertaste < 8 &
                                              coffees_train$Cupper.Points == 10))
identical(sort(coffees_outliers_flavor),sort(coffees_outliers_aftertaste))
```
They were exactly the same outliers.

Balance:
```{r fig.width=5, fig.height=4}
ggplot(coffees_train,
       aes(x = Cupper.Points,
           y = Balance)) +
  geom_point(col = "blue") +
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw()
```

4 clear outliers - Cupper.Points = 10 and Balance = 7 ; Balance > 7.5 and 
Cupper.Points < 5.5.

```{r}
coffees_outliers_balance <- which(coffees_train$Balance == 7 &
                                    coffees_train$Cupper.Points == 10)
# Actually there are 2 outliers with exact value of Balance and Cupper.Points
coffees_outliers_balance <- append(coffees_outliers_balance,
                                   which(coffees_train$Balance > 7.5 &
                                           coffees_train$Cupper.Points < 5.5))
identical(sort(coffees_outliers_flavor),sort(coffees_outliers_balance))
```
They were exactly the same outliers.

Aroma:
```{r fig.width=5, fig.height=4}
ggplot(coffees_train,
       aes(x = Cupper.Points,
           y = Aroma)) +
  geom_point(col = "blue") +
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw()
```

4 clear new outliers - Cupper.Points = 10 and Aroma < 7.75 ; Cupper.Points < 5.5 
and Aroma > 7.5.
```{r}
coffees_outliers_aroma <- which(coffees_train$Aroma < 7.75 &
                                  coffees_train$Cupper.Points == 10)
coffees_outliers_aroma <- append(coffees_outliers_aroma,
                                   which(coffees_train$Aroma > 7.5 &
                                           coffees_train$Cupper.Points < 5.5))
```
These outliers were marked earlier.

Acidity:
```{r fig.width=5, fig.height=4}
ggplot(coffees_train,
       aes(x = Cupper.Points,
           y = Acidity)) +
  geom_point(col = "blue") +
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw()
```

At least 2 clear outliers.
```{r}
which(coffees_train$Acidity < 7.5 & coffees_train$Cupper.Points == 10)
# 2 outliers marked earlier
coffees_outliers_acidity <- which(coffees_train$Acidity < 5.5 &
                                    coffees_train$Cupper.Points > 7.5)
# 1 new outlier
coffees_outliers <- append(coffees_outliers,coffees_outliers_acidity)
```

Body:
```{r fig.width=5, fig.height=4}
ggplot(coffees_train,
       aes(x = Cupper.Points,
           y = Body)) +
  geom_point(col = "blue") +
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw()
#At least 2 clear outliers
#which(coffees_train$Body == 7 & coffees_train$Cupper.Points == 10)
# 2 outliers marked earlier
coffees_outliers_body <- which(coffees_train$Body < 5.5 &
                                 coffees_train$Cupper.Points > 7.5)
# 1 new outlier
coffees_outliers <- append(coffees_outliers,coffees_outliers_body)
```

Uniformity:
```{r fig.width=5, fig.height=4}
ggplot(coffees_train,
       aes(x = Cupper.Points,
           y = Uniformity)) +
  geom_point(col = "blue") +
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw()
```

Relationship looks more like relationship with categorical variable.

Moisture:
```{r fig.width=5, fig.height=4}
ggplot(coffees_train,
       aes(x = Cupper.Points,
           y = Moisture)) +
  geom_point(col = "blue") +
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw()
```

Many values far from relationship.

Category.One.Defects:
```{r fig.width=5, fig.height=4}
ggplot(coffees_train,
       aes(x = Cupper.Points,
           y = Category.One.Defects)) +
  geom_point(col = "blue") +
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw()
```

3 clear outliers - Defects >= 15 and Cupper.Points above 6.5.
```{r}
coffees_outliers_cat1_defects <- which(coffees_train$Category.One.Defects >= 15 &
                                         coffees_train$Cupper.Points > 6.5)
coffees_outliers <- append(coffees_outliers,coffees_outliers_cat1_defects)
```

Altitude_mean_meters.impute_median:
```{r fig.width=5, fig.height=4}
ggplot(coffees_train,
       aes(x = Cupper.Points,
           y = altitude_mean_meters.impute_median)) +
  geom_point(col = "blue") +
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw()
```

There is some positive relationship, but very unclear - many values far from 
relationship.

Now I try to find highly correlated variables:
```{r}
findCorrelation(coffee_correlations,
                cutoff = 0.80,
                names = TRUE)
```
These variables are potential candidates to be excluded from the model because 
of the high correlation between them.

```{r fig.width=5, fig.height=4}
coffees_categorical_vars <-
  sapply(coffees_train, is.factor) %>% 
  which() %>% 
  names()

coffees_categorical_vars
```

I use the function that retrieves F statistic value for the explanatory 
categorical variable provided as the function argument.
```{r}
coffees_F_anova <- function(categorical_var) {
  anova_ <- aov(coffees_train$Cupper.Points ~ 
                  coffees_train[[categorical_var]]) 
  
  return(summary(anova_)[[1]][1, 4])
}
```

Relationship between coffees_categorical_vars and Cupper.Points:
```{r}
sapply(coffees_categorical_vars,
       coffees_F_anova) %>% 
  sort(decreasing = TRUE) -> coffees_anova_all_categorical

coffees_anova_all_categorical
```

Relation between Color.impute.Gmode levels and Cupper.Points:
```{r fig.width=5, fig.height=4}
ggplot(coffees_train,
       aes(x = Color.impute.Gmode,
           y = Cupper.Points)) +
  geom_boxplot(fill = "red") +
  theme_bw()
```

Green has many outliers. Bluish-Green has slightly higher values. 

Relation between Country.of.Origin.impute.Gmode levels and Cupper.Points:
```{r fig.width=8, fig.height=6}
ggplot(coffees_train,
       aes(x = Country.of.Origin.impute.Gmode,
           y = Cupper.Points)) +
  geom_boxplot(fill = "red") +
  theme(axis.text.x = element_text(angle = 60))
```

There can be seen some relationships between these variables but there are 
countries with only few coffees. Thus, we probably choose the region. 
```{r fig.width=7, fig.height=3}
ggplot(coffees_train,
       aes(x = Region,
           y = Cupper.Points)) +
  geom_boxplot(fill = "red") +
  theme_bw()
```

It can be seen that there are differences between Regions.

The relationship between Cupper.Points and Variety.impute.Gmode:
```{r fig.width=7, fig.height=4}
ggplot(coffees_train,
       aes(x = Variety.impute.Gmode,
           y = Cupper.Points)) +
  geom_boxplot(fill = "red") +
  theme(axis.text.x = element_text(angle = 45))
```

There are some differences between varieties of coffee, but not very clear.

The relationship between Cupper.Points and Processing.Method.impute.Gmode:
```{r fig.width=7, fig.height=4}
ggplot(coffees_train,
       aes(x = Processing.Method.impute.Gmode,
           y = Cupper.Points)) +
  geom_boxplot(fill = "red") +
  theme_bw()
```

There is no clear differences betweend processing methods. There are many values 
far from mean and median in Washed / Wet.

The relationship between Cupper.Points and Clean.Cup:
```{r fig.width=5, fig.height=3}
ggplot(coffees_train,
       aes(x = Clean.Cup,
           y = Cupper.Points)) +
  geom_boxplot(fill = "red") +
  theme_bw()
```

Clean.Cup = 10 has higher values than <10, but also many outliers there.

The relationship between Cupper.Points and Sweetness:
```{r fig.width=5, fig.height=3}
ggplot(coffees_train,
       aes(x = Sweetness,
           y = Cupper.Points)) +
  geom_boxplot(fill = "red") +
  theme_bw()
```

Sweetness = 10 has slightly higher values than <10, but also many outliers there.

The relationship between Cupper.Points and Quakers:
```{r fig.width=5, fig.height=3}
ggplot(coffees_train,
       aes(x = Quakers,
           y = Cupper.Points)) +
  geom_boxplot(fill = "red") +
  theme_bw()
```

Very Similar mean and similar distributions, but many outliers for Quakers = 0.

The relationship between Cupper.Points and unit_of_measurement.
```{r fig.width=5, fig.height=3}
ggplot(coffees_train,
       aes(x = unit_of_measurement,
           y = Cupper.Points)) +
  geom_boxplot(fill = "red") +
  theme_bw()
```

The relationship between Cupper.Points and Bag.Weight
```{r fig.width=5, fig.height=3}
ggplot(coffees_train,
       aes(x = Bag.Weight,
           y = Cupper.Points)) +
  geom_boxplot(fill = "red") +
  theme_bw()
```

There are diffrences between Bag.Weights, but not so big.

Bag.Weight and unit_of_measurement can be also higly correlated with 
Processing_method and Region.
Let's check it with the Cramer's V coefficient.

```{r}
DescTools::CramerV(coffees_train$unit_of_measurement,
                   coffees_train$Region)
```
Moderate association between unit_of_measurement and Region.

```{r}
DescTools::CramerV(coffees_train$unit_of_measurement,
                   coffees_train$Processing.Method.impute.Gmode)
```
Low association between unit_of_measurement and Processing.Method.impute.Gmode.

```{r}
DescTools::CramerV(coffees_train$Bag.Weight,
                   coffees_train$Region)
```
Moderate association between Bag.Weight and Region.

```{r}
DescTools::CramerV(coffees_train$Bag.Weight,
                   coffees_train$Processing.Method.impute.Gmode)
```
Low association between Bag.Weight and Processing.Method.impute.Gmode.

```{r}
DescTools::CramerV(coffees_train$Bag.Weight,
                   coffees_train$unit_of_measurement)
```
Low association between Bag.Weight and unit_of_measurement.


There is moderate association between Bag.Weight and Region and also between unit_of_measurement and Region. I do not exclude them from the analysis for now.

I check if there is some linear combination of other variables
```{r}
( findLinearCombos(coffees_train[, coffees_numeric_vars] ) ->
    coffees_linearCombos )
```
There is no such combination.

Now i prepare vector of coffee variables names.
```{r}
#all coffees_train variables
coffees_variables_all <- names(coffees_train)
```

Altitudes are very highly correlated to each other, so I choose only altitude_mean_meters.impute_median.
```{r}
coffees_variables_all <-
  coffees_variables_all[!coffees_variables_all %in% 
                          c("altitude_low_meters.impute_median",
                            "altitude_high_meters.impute_median",
                            "Category.One.Defects",
                            "Number.of.Bags")]
```

Now I delete outliers form training set.
```{r}
coffees_train <- coffees_train[-coffees_outliers,]

options(contrasts = c("contr.treatment",
                      "contr.treatment"))
```

# Data modelling

## Linear model

Estimation of the model with all variables:
```{r}
coffees_lm1 <- lm(Cupper.Points ~ ., 
                 data = coffees_train %>% 
                   dplyr::select(all_of(coffees_variables_all)))


summary(coffees_lm1)
```
There are some missing coefficients.
```{r}
coef(coffees_lm1)[is.na(coef(coffees_lm1))]
```
Unfortunately all of Region dummies seems to be multicollinear. Thus, I create 
new vector without these variables.

```{r}
coffees_variables_all2 <-
  coffees_variables_all[-which(coffees_variables_all %in% 
                                c("Region","Country.of.Origin.impute.Gmode"))]

coffees_lm2 <- lm(Cupper.Points ~ .,
                  data = coffees_train %>% 
                    dplyr::select(all_of(coffees_variables_all2)))

summary(coffees_lm2)
```
After delete the Region and Country variable R-squared has not changed.

Now I run Backward Elimination based on p-value 0.1 on both models:
```{r}
coffees_lm_backward_1 <- 
  ols_step_backward_p(coffees_lm1,
                      prem = 0.1,
                      progress = FALSE)

coffees_lm_backward_2 <- 
  ols_step_backward_p(coffees_lm2,
                      prem = 0.1,
                      progress = FALSE)
```

Final model details:
```{r}
summary(coffees_lm_backward_1$model)
summary(coffees_lm_backward_2$model)

coffees_variables_backward_1 <-
  coffees_variables_all[-which(coffees_variables_all %in% 
                                 coffees_lm_backward_1$removed)]

coffees_variables_backward_2 <-
  coffees_variables_all[-which(coffees_variables_all %in% 
                                 coffees_lm_backward_2$removed)]
```

Residuals:
```{r}
par(mfrow=c(2,2))
hist(coffees_lm1$residuals, breaks = 30, main = "Coffees_lm1")
hist(coffees_lm2$residuals, breaks = 30, main = "Coffees_lm2")
hist(coffees_lm_backward_1$model$residuals, breaks = 30, main = "Coffees_backward_lm1")
hist(coffees_lm_backward_2$model$residuals, breaks = 30, main = "Coffees_backward_lm2")

```

Model stats:
```{r}
lm_forcasts <-
  data.frame(
    regr_metrics_lm1 = predict(coffees_lm1),
    regr_metrics_lm2 = predict(coffees_lm2),
    regr_metrics_backward1 = predict(coffees_lm_backward_1$model),
    regr_metrics_backward2 = predict(coffees_lm_backward_2$model)
    )

sapply(lm_forcasts,
       function(x) regressionMetrics(real = coffees_train$Cupper.Points,
                                        predicted = x))
```
Now I create controls for cross validation:
```{r}
ctrl_cv2 <- trainControl(method = "cv",
                          number = 2)

ctrl_cv10 <- trainControl(method = "cv",
                          number = 10)
```

## GLM model
I estimate the General Linear Model with all variables and without Region and
Country variables:
```{r warning=FALSE}
set.seed(987654321)

coffees_glm_1_cv2 <- 
  train(Cupper.Points ~ .,
        data = coffees_train %>% 
          dplyr::select(all_of(coffees_variables_all)),
        method = "glm",
        metric = "RMSE",
        trControl = ctrl_cv2)

coffees_glm_1_cv10 <- 
  train(Cupper.Points ~ .,
        data = coffees_train %>% 
          dplyr::select(all_of(coffees_variables_all)),
        method = "glm",
        metric = "RMSE",
        trControl = ctrl_cv10)

coffees_glm_2_cv2 <- 
  train(Cupper.Points ~ .,
        data = coffees_train %>% 
          dplyr::select(all_of(coffees_variables_all2)),
        method = "glm",
        metric = "RMSE",
        trControl = ctrl_cv2)

coffees_glm_2_cv10 <- 
  train(Cupper.Points ~ .,
        data = coffees_train %>% 
          dplyr::select(all_of(coffees_variables_all2)),
        method = "glm",
        metric = "RMSE",
        trControl = ctrl_cv10)


```

## KNN model

```{r}
set.seed(987654321)

coffees_knn_1_cv2 <- 
  train(Cupper.Points ~ .,
        data = coffees_train %>% 
          dplyr::select(all_of(coffees_variables_all)),
        method = "knn",
        metric = "RMSE",
        trControl = ctrl_cv2)

coffees_knn_1_cv10 <- 
  train(Cupper.Points ~ .,
        data = coffees_train %>% 
          dplyr::select(all_of(coffees_variables_all)),
        method = "knn",
        metric = "RMSE",
        trControl = ctrl_cv10)

coffees_knn_2_cv2 <- 
  train(Cupper.Points ~ .,
        data = coffees_train %>% 
          dplyr::select(all_of(coffees_variables_all2)),
        method = "knn",
        metric = "RMSE",
        trControl = ctrl_cv2)

coffees_knn_2_cv10 <- 
  train(Cupper.Points ~ .,
        data = coffees_train %>% 
          dplyr::select(all_of(coffees_variables_all2)),
        method = "knn",
        metric = "RMSE",
        trControl = ctrl_cv10)
```

## LASSO Model
```{r warning=FALSE}
parameters_lasso <- expand.grid(alpha = 1,
                                lambda = seq(10, 1e5, 100))


set.seed(123456789)

coffees_lasso <-  train(Cupper.Points ~ .,
                       data = coffees_train %>% 
                         dplyr::select(all_of(coffees_variables_all)),
                       method = "glmnet", 
                       tuneGrid = parameters_lasso,
                       trControl = ctrl_cv10)
```
Models comparison:
```{r warning=FALSE}


models_forcasts <-
  data.frame(
    GLM1 = predict(coffees_glm_1_cv10,coffees_test),
    GLM2 = predict(coffees_glm_2_cv10,coffees_test),
    KNN1 = predict(coffees_knn_1_cv10,coffees_test),
    KNN2 = predict(coffees_knn_2_cv10,coffees_test),
    LASSO = predict(coffees_lasso,coffees_test)
    )

sapply(models_forcasts,
       function(x) regressionMetrics(real = coffees_test$Cupper.Points,
                                        predicted = x))
```

```{r}
resample_results <- resamples(list(GLM1=coffees_glm_1_cv10,
                                   GLM2=coffees_glm_2_cv10,
                                   KNN1=coffees_knn_1_cv10,
                                   KNN2=coffees_knn_2_cv10,
                                   LASSO=coffees_lasso
                                   ))

bwplot(resample_results , metric = c("RMSE","MAE"))
```

# Summary
It looks, that the best models are linear models. They have lower values of MAE,
RMSE and MSE.

